\section{Introduction}
Computer aided evolution(CAE) applies concepts from the domain of evolutionary
biology to problems in, for example, mathematics and computer science, in the
sense that it simulates Darwinistic evolution and natural selection.

Genetic algorithms provide a Darwinian framework for local search algorithms.
Dividing the sub problems of optimization into encoding, selection,
reproduction, and evaluation. In this transformation from the real world of
biological evolution, to CAE, there is no inherent limitation binding CAE to
software. It is possible to use these techniques on a computer, while solving
problems "in the real world". That is, we can take our experiments from \emph{in
silico} to \emph{in materio}\cite{paper:ev3}.

Ultimately the goal with such evolution in our case is to develop candidates
which are not the most obvious design choices from a human perspective, but
score a higher grade compared to already known solutions.

Building from such previous experiences, that something which usually has a
standardized morphology can get so fundamentally different results when applying
CAE, leads us to wanting to apply such methodology to other domains.

The chosen domain is within furniture, namely the types which should be suited
for seating.

One might wonder why this is relevant in our current time or in the future?

By being able to produce solutions which are outside of traditional design norms
some of the problems in modern society can be dealt with, problems such as high
resource consumption and strain on the environment when treating the resources.

Since there is a finite amount of raw materials and treatment of aforementioned
resources in the general case results in strain on the environment be it
foraging for wood or producing plastics this project is deemed highly relevant.
\todo[inline]{I would scratch this, and justify the evo of furniture with the
claim that it is a classical design issue, and that it is complex enough to test
the bounderies (maybe too strong a claim) of evolution}

By tweaking the parameters to optimize for material or comfort, the candidate
solutions might provide some very interesting and hopefully revolutionary
designs.

Designs which ultimately might save the world. \todo[inline]{No world saving and
revolutionizing please, such claims only antagonize the people who actually work
in the field}
